---
title: "Fermentation Database"
runtime: shiny
output: html_document
header-includes:
    - \usepackage{fancyhdr}
    - \usepackage{color}
    - \usepackage[margin=1in ]{geometry}
fig_caption: true
---
\addtolength{\headheight}{1.0cm} 
\setlength\headheight{28pt}
\pagestyle{fancyplain} 
\rhead{\includegraphics[height=1.2cm]{~/Desktop/mm.png}}
\renewcommand{\headrulewidth}{0pt} 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



## Biomass yield:
Please use the slider to select a date range:

```{r eruptions, echo=FALSE, warning=FALSE, comment=FALSE, message= FALSE,fig.align='center',out.extra='angle=0'}

sliderInput("date",
                  "Fermentation range",
                  min = as.Date("2017-10-17","%Y-%m-%d"),
                  max = as.Date("2018-01-30","%Y-%m-%d"),
                  value=as.Date(c("2017-10-17","2018-01-30")),timeFormat="%Y-%m-%d")
    

library(data.table)
library(readxl)
library(reshape)
library(ggplot2)
library(ggpmisc)
run<- "PB180123"
fdb<-as.data.frame(read_excel("~/Dropbox (Modern Meadow)/Modern Meadow TEAM/LEATHER/Process Development/Upstream/2017 Fermentation/Ferm data analysis/Incyght/inCyght upload folder/inCyght offline .xlsx"))
colnames(fdb)[c(40,42)]<- c("Pre-Col (g/L)", "Pop-Col (g/L)")
fdb$cond<- ifelse(fdb$`Run name` != run , "Past weeks", "Current week")
fdb$date<- as.Date(substr(fdb$`Run name`,3,100), format = "%y%m%d")
pb<- subset(fdb, fdb$`Run name` == run)
rownames(pb)<- 1:nrow(pb)
pb[c(36:42),28] <-pb[c(29:35),28]
group<- list(a = c("SU1", "SU2"), b = c("SU3", "SU4"), c = c("SU5", "SU6"))
conditions<-c("Control", "SU3,4", "SU5,6")
su<-list()
stoc<- list()
kin<- list()
titer<- list()

for (i in 1: length(group)) {
  tmp<-list()
  for (j in 1:length(group[[i]])) {
    tmp[[j]]<- subset(pb, pb$Ferm == group[[i]][j])
  }
  su[[i]]<-as.data.frame(do.call(rbind,tmp))
  colnames(su[[i]])[5]<- "time"
  stoc[[i]]<- as.data.frame(su[[i]][,c(5,7,36,11,12,27:33)])
  stoc[[i]]$RQ<- stoc[[i]][,6]*32/stoc[[i]][,7]/44
  kin[[i]]<- as.data.frame(su[[i]][,c(5,39,17)])
  kin[[i]]$`sp. Gly uptake (g/g/hr)`<-as.numeric(kin[[i]]$`sp. Gly uptake (g/g/hr)`)

}

for (i in 1:2) {
    
  titer[[i]]<- as.data.frame(subset(su[[i]],su[[i]]$time>62)[,c(4,40,41,42,43)])
  titer[[i]]<- titer[[i]][!is.na(titer[[i]][,3]),]
  titer[[i]]<-as.data.frame(cbind(melt(titer[[i]][,c(1,2,4)]),melt(titer[[i]][,c(1,3,5)])$value) )
  colnames(titer[[i]])[4]<-"sd"
  
}


renderPlot({
  yield<-subset(fdb, fdb$`EFT (hrs)`>  62)[,c(3,4,32,62,63)]; colnames(yield)[1]<- "run"
yield$runid<- paste(yield$run, yield$Ferm)
yield<- subset(yield,date >= as.Date(input$date[1], format = "%Y-%m-%d" ))
yield<- subset(yield,date <= as.Date(input$date[2], format = "%Y-%m-%d" ))
ggplot(yield, aes(run, yield$`Yx/C`))+
  geom_col(aes(fill= factor(Ferm), group = factor(Ferm)), position = "dodge")+
  xlab("")+ylab("Y X/C")+
  theme(legend.title = element_blank(),
        axis.text.x = element_text(angle = 90, size = 15),
        axis.text.y = element_text( size = 15),
        axis.title = element_text(size =15))
})


```

## Collagen titer:
Please use the slider to select a date range:
```{r , echo=FALSE, warning=FALSE, comment=FALSE, message= FALSE,fig.align='center',out.extra='angle=0'}

sliderInput("date1",
                  "Fermentation range",
                  min = as.Date("2017-10-17","%Y-%m-%d"),
                  max = as.Date("2018-01-30","%Y-%m-%d"),
                  value=as.Date(c("2017-10-17","2018-01-30")),timeFormat="%Y-%m-%d")

renderPlot({
his<-cbind(melt(fdb[,c(3,40,42,62)]), melt(fdb[,c(40,42,4)])[,1])
colnames(his)[c(1,5)]<- c("run","ferm")
his$runid<- paste(his$run,his$ferm)
his<- his[!is.na(his$run),]
his$date<- as.Date(substr(his$run,3,100),format = "%y%m%d")

his<- subset(his,date >= as.Date(input$date1[1], format = "%Y-%m-%d" ))
his<- subset(his,date <= as.Date(input$date1[2], format = "%Y-%m-%d" ))
ggplot(his, aes(reorder(run,value), value))+
  geom_col(aes(fill= factor(ferm), group =factor(ferm)), position = "dodge")+
  facet_wrap(~variable, scales = "free", ncol =2)+
  xlab("")+ylab("Titer g/L")+
  theme(legend.title = element_blank(),
        axis.text.x = element_text(angle = 90, size = 15),axis.text.y = element_text( size = 15),
        axis.title = element_text(size =15))
})
```


## Stoichiometric parameters:
```{r , echo=FALSE, warning=FALSE, comment=FALSE, message= FALSE,fig.align='center',out.extra='angle=0'}

selectInput("runid",
                  label ="Select Run ID",
                  choices = unique(fdb$`Run name`),
                  selected =  as.character(fdb[nrow(fdb),3]))

renderPlot({
run<- input$runid
fdb<-as.data.frame(read_excel("~/Dropbox (Modern Meadow)/Modern Meadow TEAM/LEATHER/Process Development/Upstream/2017 Fermentation/Ferm data analysis/Incyght/inCyght upload folder/inCyght offline .xlsx"))
colnames(fdb)[c(40,42)]<- c("Pre-Col (g/L)", "Pop-Col (g/L)")
fdb$date<- as.Date(substr(fdb$`Run name`,3,100), format = "%y%m%d")
fdb$runid<- paste(fdb$`Run name`,fdb$Ferm)
pb<- subset(fdb, fdb$`Run name` == run)
rownames(pb)<- 1:nrow(pb)
pb.s<- as.data.frame(pb[,c(4,5,7,36,11,12,27:33)]);colnames(pb.s)[2]<- "time"
pb.k<- as.data.frame(pb[,c(4,5,39,17)]);colnames(pb.k)[2]<- "time"

pb.s.m<- cbind(melt(pb.s[,-1], id.vars = "time"),melt(pb.s[,-2], id.vars = "Ferm")$Ferm);colnames(pb.s.m)[4]<- "Ferm"
pb.s.m<- subset(pb.s.m, value>= 0 & value <1000)
ggplot(pb.s.m,aes(time, value))+
  geom_point(aes(color= factor(Ferm)))+
  geom_line(aes(color= factor(Ferm)))+
  facet_wrap(~variable, scales = "free")+
  xlab("Time(h)")+ylab("")+ theme(legend.title = element_blank(),
        axis.text.x = element_text(angle = 90, size = 15),axis.text.y = element_text( size = 15),
        axis.title = element_text(size =15))
})
```
## Kinetic parameters:
```{r , echo=FALSE, warning=FALSE, comment=FALSE, message= FALSE,fig.align='center',out.extra='angle=0'}

selectInput("runid1",
                  label ="Select Run ID",
                  choices = unique(fdb$`Run name`),
                  selected =  as.character(fdb[nrow(fdb),3]))

renderPlot({
run<- input$runid1
fdb<-as.data.frame(read_excel("~/Dropbox (Modern Meadow)/Modern Meadow TEAM/LEATHER/Process Development/Upstream/2017 Fermentation/Ferm data analysis/Incyght/inCyght upload folder/inCyght offline .xlsx"))
colnames(fdb)[c(40,42)]<- c("Pre-Col (g/L)", "Pop-Col (g/L)")
fdb$date<- as.Date(substr(fdb$`Run name`,3,100), format = "%y%m%d")
fdb$runid<- paste(fdb$`Run name`,fdb$Ferm)
pb<- subset(fdb, fdb$`Run name` == run)
rownames(pb)<- 1:nrow(pb)
pb.s<- as.data.frame(pb[,c(4,5,7,36,11,12,27:33)]);colnames(pb.s)[2]<- "time"
pb.k<- as.data.frame(pb[,c(4,5,39,17)]);colnames(pb.k)[2]<- "time"

pb.k.m<- cbind(melt(pb.k[,-1], id.vars = "time"),melt(pb.k[,-2], id.vars = "Ferm")$Ferm);colnames(pb.k.m)[4]<- "Ferm"
pb.k.m$value<- as.numeric(pb.k.m$value)
ggplot(pb.k.m,aes(time, value))+
  geom_point(aes(color= factor(Ferm)))+
  geom_line(aes(color= factor(Ferm)))+
  facet_wrap(~variable, scales = "free")+
  theme(legend.title = element_blank(),
        axis.text.x = element_text(angle = 90, size = 15),axis.text.y = element_text( size = 15),
        axis.title = element_text(size =15))

})
```

## Biomass yield:
Please use the slider to select a date range:

```{r , echo=FALSE, warning=FALSE, comment=FALSE, message= FALSE,fig.align='center',out.extra='angle=0'}

sliderInput("date2",
                  "Fermentation range",
                  min = as.Date("2017-10-17","%Y-%m-%d"),
                  max = as.Date("2018-01-30","%Y-%m-%d"),
                  value=as.Date(c("2017-10-17","2018-01-30")),timeFormat="%Y-%m-%d")
    
sliderInput("y1",
                  "Select Fermentations with Yield greater than",
                  min = 0,
                  max = 1,
                  value= 0)

sliderInput("b1",
                  "Select Fermentations with final WCW concentration greater than",
                  min = 0,
                  max = 600,
                  value= 0)




renderPlot({

  fdb<-as.data.frame(read_excel("~/Dropbox (Modern Meadow)/Modern Meadow TEAM/LEATHER/Process Development/Upstream/2017 Fermentation/Ferm data analysis/Incyght/inCyght upload folder/inCyght offline .xlsx"))
colnames(fdb)[c(40,42)]<- c("Pre-Col (g/L)", "Pop-Col (g/L)")
fdb$date<- as.Date(substr(fdb$`Run name`,3,100), format = "%y%m%d")
fdb$runid<- paste(fdb$`Run name`,fdb$Ferm)
y<- unique(subset(fdb, fdb$`EFT (hrs)`>62 & fdb$`Yx/C` >= input$y1)$runid)
b<- unique(subset(fdb, fdb$`EFT (hrs)`>62 & fdb$`WCW (g/L)` >= input$b1)$runid)
k<- intersect(y,b)
fdb<-fdb[fdb$runid %in% k,]
pb<- subset(fdb,date >= as.Date(input$date2[1], format = "%Y-%m-%d" ))
pb<- subset(pb,date <= as.Date(input$date2[2], format = "%Y-%m-%d" ))


rownames(pb)<- 1:nrow(pb)
pb.s<- as.data.frame(pb[,c(63,5,7,36,11,12,27:33)] );colnames(pb.s)[c(1,2)]<- c("Ferm","time")
pb.k<- as.data.frame(pb[,c(63,5,39,17)]);colnames(pb.k)[c(1,2)]<- c("Ferm","time")

pb.s.m<- cbind(melt(pb.s[,-1], id.vars = "time"),melt(pb.s[,-2], id.vars = "Ferm")$Ferm);colnames(pb.s.m)[4]<- "Ferm"
pb.s.m<- subset(pb.s.m, value>= 0 & value <1000)
ggplot(pb.s.m,aes(time, value))+
  geom_point(aes(color= factor(Ferm)))+
  geom_line(aes(color= factor(Ferm)))+
  facet_wrap(~variable, scales = "free")+
  xlab("Time(h)")+ylab("")+ theme(legend.title = element_blank(),
        axis.text.x = element_text(angle = 90, size = 15),axis.text.y = element_text( size = 15),
        axis.title = element_text(size =15))
})


```

```{r , echo=FALSE, warning=FALSE, comment=FALSE, message= FALSE,fig.align='center',out.extra='angle=0'}

sliderInput("date3",
                  "Fermentation range",
                  min = as.Date("2017-10-17","%Y-%m-%d"),
                  max = as.Date("2018-01-30","%Y-%m-%d"),
                  value=as.Date(c("2017-10-17","2018-01-30")),timeFormat="%Y-%m-%d")
    

sliderInput("y2",
                  "Select Fermentations with Yield greater than",
                  min = 0,
                  max = 1,
                  value= 0)

sliderInput("b2",
                  "Select Fermentations with final WCW concentration greater than",
                  min = 0,
                  max = 600,
                  value= 0)



renderPlot({
  fdb<-as.data.frame(read_excel("~/Dropbox (Modern Meadow)/Modern Meadow TEAM/LEATHER/Process Development/Upstream/2017 Fermentation/Ferm data analysis/Incyght/inCyght upload folder/inCyght offline .xlsx"))
colnames(fdb)[c(40,42)]<- c("Pre-Col (g/L)", "Pop-Col (g/L)")
fdb$date<- as.Date(substr(fdb$`Run name`,3,100), format = "%y%m%d")
fdb<- subset(fdb, fdb$date  <= as.Date(substr(run,3,100), format = "%y%m%d"))
fdb$runid<- paste(fdb$`Run name`,fdb$Ferm)
y<- unique(subset(fdb, fdb$`EFT (hrs)`>62 & fdb$`Yx/C` >= input$y2)$runid)
b<- unique(subset(fdb, fdb$`EFT (hrs)`>62 & fdb$`WCW (g/L)` >= input$b2)$runid)
k<- intersect(y,b)
fdb<-fdb[fdb$runid %in% k,]
pb<- subset(fdb,date >= as.Date(input$date3[1], format = "%Y-%m-%d" ))
pb<- subset(pb,date <= as.Date(input$date3[2], format = "%Y-%m-%d" ))
rownames(pb)<- 1:nrow(pb)
pb.s<- as.data.frame(pb[,c(63,5,7,36,11,12,27:33)]);colnames(pb.s)[c(1,2)]<- c("Ferm","time")
pb.k<- as.data.frame(pb[,c(63,5,39,17)]);colnames(pb.k)[c(1,2)]<- c("Ferm","time")


pb.k.m<- cbind(melt(pb.k[,-1], id.vars = "time"),melt(pb.k[,-2], id.vars = "Ferm")$Ferm);colnames(pb.k.m)[4]<- "Ferm"
pb.k.m$value<- as.numeric(pb.k.m$value)
ggplot(pb.k.m,aes(time, value))+
  geom_point(aes(color= factor(Ferm)))+
  geom_line(aes(color= factor(Ferm)))+
  facet_wrap(~variable, scales = "free")+
  xlab("Time(h)")+ylab("")+ theme(legend.title =element_blank(),
        axis.text.x = element_text(angle = 90, size = 15),axis.text.y = element_text( size = 15),
        axis.title = element_text(size =15))
})


```


## Process conditions:

```{r , echo=FALSE, warning=FALSE, comment=FALSE, message= FALSE,fig.align='center',out.extra='angle=0'}
pdb<-as.data.frame(read_excel("~/Dropbox (Modern Meadow)/Modern Meadow TEAM/LEATHER/Process Development/Upstream/2017 Fermentation/Ferm data analysis/Fermentation Process Conditions Database 16JAN18.xlsx", sheet = "Conditions"))
pdb<- pdb[,1:3]



renderDataTable({
  
   as.data.frame(pdb)

  
})

 
```